---
title: "Reproduce Examples in Righetti & Balluff 2025"
author: "Nicola Righetti & Paul Balluff"
date: "14, March 2025"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to CooRTweet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(CooRTweet)
```


This script runs examples and create network plots for the paper: 'CooRTweet: A Generalized R Software for Coordinated Network' [@Righetti2025].

The code generating the names in the plot is not working and thus commented out in this version to preserve anonymity. The data consists of climate-related posts on Facebook and Twitter during the German 2021 election campaign, subset to posts with an image where collection was possible. The data is anonymized and available in the package under the name `german_elections`.

# Threshold graphs

```{r}
library(CooRTweet)
library(data.table)
library(igraph)

# load the german_elections data 
# contains the following columns:
# - account_id (string, with shorthand for platform)
# - post_id (integer)
# - url_id (integer, anonymized url contained in post)
# - hashtag_id (integer, anonymized hashtag contained in post)
# - domain_id (integer, anonymized domain of url)
# - phash_id (integer, anonymized perceptual hash of shared image)
# - timestamp (numeric, timestamp of post)

# urls ----------------------
urls_data <- prep_data(german_elections,
                       object_id = "url_id",
                       account_id = "account_id",
                       content_id = "post_id",
                       timestamp_share = "timestamp")

urls_data <- unique(urls_data,
                    by = c("object_id", "account_id", "content_id", "timestamp_share"))

urls_data <- urls_data[!is.na(object_id)]

urls_data$object_id <- paste0("url_", urls_data$object_id)

# domains ----------------------
domains_data <- prep_data(german_elections,
                          object_id = "domain_id",
                          account_id = "account_id",
                          content_id = "post_id",
                          timestamp_share = "timestamp")

domains_data <- unique(domains_data,
                       by = c("object_id", "account_id", "content_id", "timestamp_share"))

domains_data <- domains_data[!is.na(object_id)]

domains_data$object_id <- paste0("url_", domains_data$object_id)

# hashtags ------------------
hashtag_data <- prep_data(german_elections,
                          object_id = "hashtag_id",
                          account_id = "account_id",
                          content_id = "post_id",
                          timestamp_share = "timestamp")

hashtag_data <- unique(hashtag_data,
                       by = c("object_id", "account_id", "content_id", "timestamp_share"))

hashtag_data <- hashtag_data[!is.na(object_id)]

hashtag_data$object_id <- paste0("hashtag_", hashtag_data$object_id)

# images --------------------
img_data <- prep_data(german_elections,
                      object_id = "phash_id",
                      account_id = "account_id",
                      content_id = "post_id",
                      timestamp_share = "timestamp")

img_data <- unique(img_data,
                   by = c("object_id", "account_id", "content_id", "timestamp_share"))

img_data <- img_data[!is.na(object_id)]

img_data$object_id <- paste0("hash_", img_data$object_id)

# thresholds plots -------------------------------------------------------------

fb_urls <- urls_data[grepl("fb", urls_data$account_id),]

result_urls_fb <- detect_groups(fb_urls, time_window = 60,
                                min_participation = 2)

g_urls_fb <- generate_coordinated_network(result_urls_fb,
                                          edge_weight = 0.5,
                                          objects = TRUE)

g_urls_fb


# privacy-protected -----------------------------------------------------------#
# add accounts names -----
# data not publicly available in the public version of the script 

# deanonim <- readRDS("data/german_elections_sample_non-anon.rds")
# 
# igraph::V(g_urls_fb)$username_complete <-
#   as.character(sapply(igraph::V(g_urls_fb)$name,
#                       function(x)
#                         unique(deanonim$username[deanonim$account_id == x])))
# 
# igraph::V(g_urls_fb)$username  <- substr(igraph::V(g_urls_fb)$username_complete, 1, 15)
# -----------------------------------------------------------------------------#

if (!dir.exists("graphs")) {
  dir.create("graphs")
}

pdf("graphs/threshold-graphs.pdf", paper = "A4r", width = 11.7, height = 5)

par(mar = c(2, 1, 2, 2))  
par(oma = c(0, 0, 0, 0))  

par(family = "Helvetica")

par(mfrow=c(1,3))

plot.igraph(
  g_urls_fb,
  layout = layout.fruchterman.reingold,
  edge.width = 0.5,
  edge.curved = 0.4,
  vertex.color = ifelse(E(g_urls_fb)$weight_threshold == 1, "orange", "tomato"),
  vertex.size = 3,
  vertex.frame.width = 0.05,
  vertex.frame.color = "grey",
  vertex.label = NA
)

mtext("Edge-weight Threshold Network", side = 1, line = 0.01, cex = 0.8, adj = 0.5)  

legend(
  "topright",
  y = 3,  
  legend = c("meets edge-weight threshold", "does not meet edge-weight threshold"),
  col = c("orange", "tomato"),
  pch = 19,
  pt.cex = 1.5,
  bty = "n",
  y.intersp = 1
) 

# privacy-protected -----------------------------------------------------------#
# de-anonimized data unavailable in the public version of this script

# Subset to "FOCUS" accounts ----

# focus_vertices <- V(g_urls_fb)[grepl("focus online", V(g_urls_fb)$username, ignore.case = T)]
# 
# g_components <- components(g_urls_fb) 
# community_id <- g_components$membership[focus_vertices]
# community_vertices <- V(g_urls_fb)[g_components$membership == community_id[1]]
# focus_subgraph <- subgraph(g_urls_fb, community_vertices)


# # Plot the subgraph
# plot.igraph(
#   focus_subgraph,
#   layout = layout.fruchterman.reingold,
#   edge.width = 0.2,
#   edge.alpha = 0.1,
#   edge.curved = 0.4,
#   vertex.color = ifelse(E(focus_subgraph)$weight_threshold == 1, "orange", "tomato"),
#   vertex.size = 6,
#   vertex.frame.width = 0.1,
#   vertex.frame.color = "grey",
#   vertex.label = V(focus_subgraph)$username_complete,
#   vertex.label.family = "sans",
#   vertex.label.cex = 0.3,
#   vertex.label.color = "grey20"
# )
# 
# mtext("Edge-weight Threshold Network (Subset)", side = 1, line = 0.01, cex = 0.8, adj = 0.5)  # Move title closer
# -----------------------------------------------------------------------------#

## fast network -----

results_urls_fb_fast <- flag_speed_share(fb_urls, 
                                   result = result_urls_fb,
                                   time_window = 10,
                                   min_participation = 2)

g_urls_fb_fast <- generate_coordinated_network(results_urls_fb_fast,
                                               fast_net = TRUE,
                                               edge_weight = 0.5,
                                               subgraph = 0)


edge_ids <- E(g_urls_fb_fast)[E(g_urls_fb_fast)$weight_threshold_full == 1]
g_urls_fb_fast <- subgraph.edges(g_urls_fb_fast, edge_ids)

# privacy-protected -----------------------------------------------------------#
# Subset to "FOCUS" accounts
# de-anonimized data unavailable in the public version of the script
# igraph::V(g_urls_fb_fast)$username_complete <-
#   as.character(sapply(igraph::V(g_urls_fb_fast)$name,
#                       function(x)
#                         unique(deanonim$username[deanonim$account_id == x])))

# igraph::V(g_urls_fb_fast)$username  <- substr(igraph::V(g_urls_fb_fast)$username_complete, 1, 15)

# focus_vertices <- V(g_urls_fb_fast)[grepl("Focus online", V(g_urls_fb_fast)$username, ignore.case = T)]

# g_components <- components(g_urls_fb_fast) 
# community_id <- g_components$membership[focus_vertices]
# community_vertices <- V(g_urls_fb_fast)[g_components$membership == community_id[1]]
# focus_subgraph_fast <- subgraph(g_urls_fb_fast, community_vertices)

# plot.igraph(
#   focus_subgraph_fast,
#   layout = layout.fruchterman.reingold,
#   edge.width = 0.2,
#   edge.curved = 0.4,
#   vertex.color = ifelse(E(focus_subgraph_fast)$weight_threshold_fast == 1, "gold", 
#                         ifelse(E(focus_subgraph_fast)$weight_threshold_full == 1, "orange",
#                                "navy")),
#   vertex.size = 6,
#   vertex.frame.width = 0.1,
#   vertex.frame.color = "grey",
#   # vertex.label.color = "grey20",
#   # vertex.label.cex = 0.3,
#   vertex.label = NA
#   # vertex.label = V(focus_subgraph_fast)$username_complete
# )
# 
# mtext("Time Threshold Network (Subset)", side = 1, line = 0.01, cex = 0.8, adj = 0.5)  
# 
# legend(
#   "topright",
#   y = 3, 
#   legend = c("<= 10 secs", "<= 30 secs"),
#   col = c("gold", "orange"),
#   pch = 19,
#   pt.cex = 1.5,
#   bty = "n",
#   y.intersp = 1
# ) 
# 
# dev.off()
# -----------------------------------------------------------------------------#

```

# Multi-platform and multi-modal graphs

```{r}

result_urls <- detect_groups(urls_data, time_window = 30,
                             min_participation = 2)

result_domains <- detect_groups(domains_data, time_window = 30,
                                min_participation = 2)

result_hashtags <- detect_groups(hashtag_data, time_window = 30,
                                 min_participation = 2)

result_images <- detect_groups(img_data, time_window = 30,
                               min_participation = 2)


combined_results <- rbindlist( 
  list(result_urls, result_domains, result_hashtags, result_images),
  use.names = TRUE,
  fill = TRUE
)

# combined graph
g <- generate_coordinated_network(combined_results,
                                  edge_weight = 0.5,
                                  subgraph = 0)


V(g)$platform <- ifelse(gsub("_.*", "", V(g)$name) == "fb", "Facebook", "Twitter")

# distinct graphs
g_urls <- generate_coordinated_network(result_urls,
                                       edge_weight = 0.25,
                                       subgraph = 1)

g_domains <- generate_coordinated_network(result_domains,
                                          edge_weight = 0.25,
                                          subgraph = 1)

g_hashtags <- generate_coordinated_network(result_hashtags,
                                           edge_weight = 0.25,
                                           subgraph = 1)

g_images <- generate_coordinated_network(result_images,
                                         edge_weight = 0.25,
                                         subgraph = 1)

V(g_urls)$platform <- ifelse(grepl("fb", V(g_urls)$name), "Facebook", 
                             ifelse(grepl("tw", V(g_urls)$name), "Twitter", "Instagram"))

V(g_domains)$platform <- ifelse(grepl("fb", V(g_domains)$name), "Facebook", 
                                ifelse(grepl("tw", V(g_domains)$name), "Twitter", "Instagram"))

V(g_hashtags)$platform <- ifelse(grepl("fb", V(g_hashtags)$name), "Facebook", 
                                 ifelse(grepl("tw", V(g_hashtags)$name), "Twitter", "Instagram"))

V(g_images)$platform <- ifelse(grepl("fb", V(g_images)$name), "Facebook", 
                               ifelse(grepl("tw", V(g_images)$name), "Twitter", "Instagram"))


pdf("graphs/multimodal-multiplatform.pdf", paper = "A4r", width = 11.7, height = 6)

par(mar = c(2, 2, 2, 2))  
par(oma = c(0, 0, 0, 0))  

par(family = "Helvetica")

layout(matrix(c(1,1,1,1,
                2,3,4,5), nrow = 2, ncol = 4))

min_degree <- 2
g_small <- induced_subgraph(g, vids = V(g)[degree(g) > min_degree])


plot.igraph(
  g_small,
  layout = layout.fruchterman.reingold,
  edge.width = 0.5,
  edge.curved = 0.3,
  vertex.color = c("Twitter" = "skyblue", "Facebook" = "navy")[V(g_small)$platform],
  vertex.size = 3,
  vertex.frame.color = "grey",
  vertex.frame.width = 0.1,
  vertex.label = NA
)

mtext("combined", side = 1, line = 0.1, cex = 1, adj = 0.5)

# Add the legend
legend(
  "topleft",
  legend = c("Twitter", "Facebook"),
  col = c("skyblue", "navy"),
  y = 1,
  pch = 19,
  pt.cex = 2,
  bty = "n",
  y.intersp = 1
) 

plot.igraph(
  g_urls,
  layout = layout.fruchterman.reingold,
  edge.width = 0.5,
  edge.curved = 0.3,
  vertex.color = c("Twitter" = "skyblue", "Facebook" = "navy")[V(g_urls)$platform],
  vertex.size = 3,
  vertex.frame.color = "grey",
  vertex.frame.width = 0.1,
  vertex.label = NA
)

mtext("urls", side = 1, line = 0.1, cex = 1, adj = 0.5)

plot.igraph(
  g_domains,
  layout = layout.fruchterman.reingold,
  edge.width = 0.5,
  edge.curved = 0.3,
  vertex.color = c("Twitter" = "skyblue", "Facebook" = "navy")[V(g_domains)$platform],
  vertex.size = 3,
  vertex.frame.color = "grey",
  vertex.frame.width = 0.1,
  vertex.label = NA
)

mtext("domains", side = 1, line = 0.1, cex = 1, adj = 0.5)

plot.igraph(
  g_hashtags,
  layout = layout.fruchterman.reingold,
  edge.width = 0.5,
  edge.curved = 0.3,
  vertex.color = c("Twitter" = "skyblue", "Facebook" = "navy")[V(g_hashtags)$platform],
  vertex.size = 3,
  vertex.frame.color = "grey",
  vertex.frame.width = 0.1,
  vertex.label = NA
)

mtext("hashtags", side = 1, line = 0.1, cex = 1, adj = 0.5)

plot.igraph(
  g_images,
  layout = layout.fruchterman.reingold,
  edge.width = 0.5,
  edge.curved = 0.3,
  vertex.color = c("Twitter" = "skyblue", "Facebook" = "navy")[V(g_images)$platform],
  vertex.size = 3,
  vertex.frame.color = "grey",
  vertex.frame.width = 0.1,
  vertex.label = NA
)

mtext("images", side = 1, line = 0.1, cex = 1, adj = 0.5)

dev.off()

rm(list = ls())
gc()
```

## References
