---
title: "Introduction to CooRTweet"
author: "Nicola Righetti & Paul Balluff"
date: ", March 2025"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Introduction to CooRTweet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(CooRTweet)
```

## Overview

The `CooRTweet` package is a powerful R tool for detecting and analyzing coordinated behavior across social media platforms. Named after Twitter, a quintessential site for coordinated message amplification through its features like hashtags and trending topics, CooRTweet is a versatile tool applicable to any social media platform, enabling analysis on mono-platform, multi-platform, and cross-platform datasets. Besides being platform-independent, it is also content-independent, supporting a wide range of content types (including hashtags, URLs, images, and any other objects of interest to the researcher). The package allows for flexible thresholds to identify coordination while also accounting for the uncoordinated network in which the coordination is contextualized. CooRTweet is one of the first software tools for coordinated detection to have undergone rigorous validation. With its output, researchers can effectively explore networks of coordinated activity.

## Installation

You can install the `CooRTweet` package from CRAN or GitHub:

```{r install, eval = FALSE}
# Install from CRAN
install.packages("CooRTweet")

# Or install the development version from GitHub
devtools::install_github("username/CooRTweet") # Replace with actual GitHub repository
```

## Key Features

1. **Flexible Data Handling**: Works with mono-modal, multi-modal, and cross-platform datasets, and any type of object.
2. **Customizable Thresholds**: Set time intervals and repetition/edge-weight thresholds to detect coordinated activities.
3. **Graph-Based Analysis**: Outputs coordination networks as `igraph` objects for further analysis and visualization.
4. **Included Data**: Comes with datasets for learning [@Kulichkina2024, @Righetti2022] and a `simulate_data` function to generate synthetic coordinated networks.

## Getting Started

### Input Data Format

The input dataset should include the following columns:

- `object_id`: A unique identifier for the shared content (data type: character).
- `account_id`: The user account identifier (data type: character).
- `content_id`: The unique ID of the post (data type: character).
- `timestamp_share`: The timestamp when the content was shared (data type: integer, UNIX format).

Example:

```{r data-preparation}
library(CooRTweet)
head(russian_coord_tweets)
```

### Detect Coordinated Groups

Use the `detect_groups()` function to find groups of accounts coordinating within a specified time window.

```{r detect-groups}
result <- detect_groups(
  x = russian_coord_tweets,
  min_participation = 2,
  time_window = 60
)
head(result)
```

### Generate Coordination Networks

Convert detected groups into a coordination network using `generate_coordinated_network()`.

```{r generate-network}
graph <- generate_coordinated_network(
  result,
  edge_weight = 0.5
)
graph
```

## Advanced Usage

### Multi-Modal and Multi-Platform Analysis

To analyze multiple types of content (e.g., URLs, hashtags), run `detect_groups()` separately for each type and combine the results.

We provide an authentic dataset from @Righetti2022 that showcases coordinated behavior during the German federal elections in 2021.

```{r german-elections}
# Example datasets for different content types
head(german_elections)
```

First we prepare shared URLs:
```{r multimodal-urls}
# URLs
urls_data <- prep_data(german_elections,
                       object_id = "url_id",
                       account_id = "account_id",
                       content_id = "post_id",
                       timestamp_share = "timestamp")

urls_data <- unique(urls_data,
                    by = c("object_id", "account_id", "content_id", "timestamp_share"))

urls_data <- urls_data[!is.na(object_id)]

urls_data$object_id <- paste0("url_", urls_data$object_id)
```

Next, we prepare images. We used the [pHash algorithm](https://en.wikipedia.org/wiki/Perceptual_hashing) to uniquely identify images. The algorithm is implemented in the `OpenImageR` package [@OpenImageR].

```{r multimodal-images}
# images (pHash)
img_data <- prep_data(german_elections,
                      object_id = "phash_id",
                      account_id = "account_id",
                      content_id = "post_id",
                      timestamp_share = "timestamp")

img_data <- unique(img_data,
                   by = c("object_id", "account_id", "content_id", "timestamp_share"))

img_data <- img_data[!is.na(object_id)]

img_data$object_id <- paste0("hash_", img_data$object_id)
```

Next, we perform the first step of coordination detection on each subset of the data with the `detect_groups` function:

```{r multimodal-detect groups}
# Detect coordinated groups for URLs and hashtags  --------------------
result_urls <- detect_groups(urls_data, time_window = 30,
                             min_participation = 2)

result_images <- detect_groups(img_data, time_window = 30,
                               min_participation = 2)

```

Then we can simply stack both resulting `data.tables`:

```{r multimodal-stack}
# Combine results  --------------------
library(data.table)

combined_results <- rbindlist( 
    list(result_urls, result_images),
    use.names = TRUE,
    fill = TRUE
)
```

Now we can let the network analysis run with the default settings to find accounts that show coordinated behavior in terms of image and URL sharing:

```{r multimodal-generate-network}
# Generate the coordinated multi-modal network  --------------------
graph <- generate_coordinated_network(combined_results, edge_weight = 0.5)
graph
```

### Visualization

Visualize the coordination network using `igraph`:

```{r visualize-network, eval = FALSE}
library(igraph)

min(E(coord_graph)$weight[E(coord_graph)$weight_threshold == 1])
```

Edge weight is not a perfect measure in an undirected graph, as it can be influenced by extreme values from a user. Therefore, an equilibrium measure, balancing the contributions of each of the two nodes on every edge, is concurrently computed. This measure, called `edge_symmetry_score`, equals 1 when the contribution is perfectly even and approaches zero in other cases.

We can quickly get some summary statistics by using the provided convenience functions `group_stats()` and `account_stats()`. If we are interested in the content that accounts share in a coordinated fashion, we can call `group_stats()` and pass in our `igraph` object from the `generate_coordinated_network` function:

```{r results='hide'}
summary_groups <- group_stats(coord_graph = coord_graph, weight_threshold = "full")
```

`summary_groups` shows how many accounts (column `num_accounts`) participated for each unique shared object (`object_id`).

If you are interested in understanding more about the users you can call `account_stats()`:

```{r results='hide'}
summary_accounts <- account_stats(coord_graph = coord_graph, result = result, weight_threshold = "full")
```

The documentation for each function includes details and possible options).

You can focus on a narrower time window by updating the result of the `detect_group` function via the `flag_speed_share` function. 

```{r}
result_update <- flag_speed_share(russian_coord_tweets, result, min_participation = 2, time_window = 120)
```

This function creates a new column marking the edges that meet the new condition. 

Using special options of the `generate_coordinated_network` function, we can get the graph of accounts who have shared content faster and whose edge are above the threshold (`subgraph = 2`). Other options allow for the general network filtered by edge weight (`subgraph = 1`) or the subgraph whose nodes exhibit coordinated behavior in the narrowest time window established with the `flag_speed_share` function (fast subgraph), and the vertices adjacent to their edges (`subgraph = 3`).

```{r}
coord_graph_fast <-
  generate_coordinated_network(
    result_update,
    fast_net = TRUE,
    edge_weight = 0.99,
    subgraph = 2
  )
```


# Using your own data

Any dataset can be utilized with CooRTweet, provided it includes the necessary data. The convenience function `prep_data` facilitates the creation of an appropriate data format for further processing. Users need only to specify the columns in their dataset corresponding to the required ones, namely, a column with the desired object to be tracked (`object_id`), the account (or user) IDs (`account_id`), the IDs of the content featuring the object (`content_id`), and the timestamps of the shares (`timestamp_share`).

```{r eval=FALSE}
prep_data <-
  function(x,
           object_id = NULL,
           account_id = NULL,
           content_id = NULL,
           timestamp_share = NULL
  )
```

## Additional features

The CooRTweet package includes several additional functions and features that enable refined exploration of coordinated networks, as detailed in the package documentation.

## Conclusion

The `CooRTweet` package enables researchers to study coordinated behaviors with a high degree of flexibility and precision. Its generalized architecture makes it adaptable to various contexts and datasets, empowering social media research and analysis.

## References
